|

### 2021-10-26 02-Chp-Systematic-Review-Tools.Rmd
Updates

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
Why are open source statistical programming  
languages the best?

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = TRUE}
Why are open source statistical programming  
languages the best?

### 2021-10-26 06-Chp-IPD-Analysis.Rmd
Updates

@@

<!-- Previous SWARs have been registered as protocols, but have not yet reported! -->

@@

<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts,  -->

>>>>

<!-- TODO Need quote for here -->

@@

<!-- Previous SWARs have been registered as protocols, but have not yet reported! - Not sure this is actually true! Double check. -->

@@

<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts, all full-scale IPD would have been logisitically challenging. It is positive that off the cohorts analysed, the majority represented new data not previously considered -->

### 2021-10-26 07-Chp-Triangulation.Rmd
Updates

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

@@

<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation. -->

@@

@@

@@

This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)

### Data sources

This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).

&nbsp;

&nbsp;

&nbsp;

### Background to the causal question

This was also guideded by the forthcoming ROBINS-E tool, which has

### Definition of the causal question

<!-- TODO See ROBINS-E for this, as to how to think about exposures -->

@@

## Terminology

@@

### Summary of triangulation

Need to check how much I talk about this in the introduction

Describe in detail

### Evidence sources

@@

In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elictation process using a number of experts.

### Risk of bias tool

@@

While the triangulation framework provides for inclusion of multiple distinct types of evidence, based on the scoping search, it is likely that the three main sources will be RCTs of statins, multivariable regression of prospective cohorts, and the use of genetic instruments in observational data (Mendelian Randomisation studies). One important difference between these approaches that will need to be addressed in the triangulation
is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this). The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course.

### Graphical representation

@@

<!----------------------------------------------------------------------------->
### Analyses

Bias-adjusted meta-analysis [@higgins2008a]

## Triangulation across exisiting evidence and evidence produced in this thesis

Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .

Summary table of different studies and results

## Qualitative vs qunatitative triangulation

### Researcher positionality statement

## Discussion of E-values

## Use of concensus panel to bring everything together

## Results

@@

@@

@@

>>>>

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:tri-quote)', echo = TRUE}
Next on my list of features to be specially considered I would place the consistency
of the observed association. Has it been repeatedly observed by different persons, in different places, circumstances and times?
```
(ref:tri-quote) --- Sir Austin Bradford Hill, 1965 [@hill1965]

@@

@@

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/helper.R")
knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
knitr::read_chunk("R/07-Code-Triangulation-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question. Different sources of evidence will have different limitations. If the result from each source points towards the same answer, this improves our confidence in the conclusion.

@@

This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \ref(cprd-heading) and IPD \ref(ipd-heading).

@@

### Terminology

__Different types of triangulation__

Qualitative triangulation is describing the different results.It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different "contexts". In this framework.

However, previous attempts at triangulation ignore the potential for varying and opposing sources of bias within a evidence source. For example,

@@

<!-- "If the aim of a meta-analysis is to summarize the literature rather than to address a target question, there is no need to adjust for external biases since differences between the (idealized) studies are accepted as diversity. The need to adjust for internal biases remains and our method can be applied directly to these." Taken from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2667303/ - good explanation on difference between qualitative and quantitative triangulation. -->

## Methods
### Data sources

This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) (statins on dementia outcomes in the CPRD) & \@ref(ipd-heading) (lipids on dementia outcomes in IPD).

Table \@ref(triSummary) illustrates the causal question each approach attempted to answer, along with the exposures and outcomes for each.

<!----------------------------------------------------------------------------->
(ref:triSummary-caption) triSummary

(ref:triSummary-scaption) triSummary

```{r triSummary-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

As a first step to assessing the evidence, all evidence sources were grouped by outcome and compared and contrasted. Potential reasons for heterogeneity were examined with specific reference to the risk of bias assessments performed.

### Quantitative triangulation

In addition to the qualitative discussion of evidence, I attempted to integrate the . This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and

#### Definition of the causal questions of interest (case-studies)
<!-- TODO See ROBINS-E for this, as to how to think about exposures -->

Background to the causal question

This was also guided by the forthcoming ROBINS-E tool, which has

•	One interventional: Effect of average exposure to LDL-c during midlife on AD 
•	One aetiological: Effect of cumulative LDL-c from birth

@@

####	Identify relevant studies

Once the causal question of interest had been defined, studies related to it were

####	Assess risk of bias in each result, define expected directions of each bias

@@

#### Visually inspect results and bias

Within our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.

Talk about new visualisation method here, and the different

@@

####	Assign modifying values to risk/direction of bias

One key feature of the domain-based risk-of-bias domains is that the domains are considered interchangeable - i.e. a high risk of bias in one domain is equivalent to a high risk fo bias in any other. This runs contrary to the idea put forward in some previous tools where certain domains

However, this also allows us to a priori define common modifying values across all domains of bias. In a bias-adjusted meta-analysis using this approach, a high risk of bias in the will have the same modifying effect on the results.

As such, a simulation approach was taken to explore the impacts of several different strategies

<!-- TODO Discuss proportional versus additive, and the fact that all biases considered previously for internal were deemed to be additive. -->

####	Assign modifying values to risk/direction of bias

"One important difference between these approaches that will need to be addressed in the triangulation is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this). The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course."

####	Combine in a bias-adjusted meta-analysis

<!-- TODO Deal with the fact that the Panel wasn't super useful -->

## Results
### Intro

@@

```{r azd-text, echo = FALSE}
```

#### All-cause dementia

#### Alzheimer's disease

#### Vascular dementia

__Impact of patient characteristics__

### Quantitative triangulation

@@

Future quantitative triangulation should move beyond the concept of comparing results at the approach leve, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question.

While this makes the process both more labour intensive and complex, to assume that, for example, all retro-spective studies are equally at risk is to overlook. While ti could be true thtat all retrospective studies share some _minimal level_ of bias, there are several opportunities. Failing to seperate these out results in a lack of information.

In this chapter, I have presented a new visualistion fo the bias inherent to each result, and suggested hwo. While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiologic studies, these do not yet exist.

### Problems with quantitative triangulation approach

Missing natural variation obtained from elicitation approach. Trade-off between systematic approach presented here and personal variation obtained from several reviewers.

A potential combination between the two would be to use the variation in risk-of-bias assessments

Eliciation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.

No good information on what the potential biases should be.

Meta-epidemiological studies on the effect of different methodological issues on results exist for randomised controlled trials,[@amer2021; @page2016] suggesting that X, Y and Z.

However, there is substantially less , arguably because of the absence of clear
Many meta-epi studies of non-randomised studies assume bias at the study-design level, similar to the early triangulation frame-work, rather than considering the actual biases deemed to be present in a given result. In this scenario, study

Potential future meta-epidemiology studies should begin to create these datasets.

A key example of a useful future study in this domain would be the mining of maximally adjusted vs. unadjusted estimates from abstracts from primary studies to assess the impact of insufficient confounding by topic. However, these datasets could also be built from systematic reviews of a topic, as they would already be gruped by reserach domain and provided the risk of bias data is shared, provide a ready source of information

For example, if it was . New software for performing risk of bias assessments, being developed by the Bristol Appraisal and review of Research group has this as a secondary methodological aim.

In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elicitation process using a number of experts.

<!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->

### Discussion of E-values

Present as an alternative to putting priors on the level of bias due to confounding. E-values work the other way around - get result then work out how strong a biasing factor would have to be to negate the result. One major problem is that they can only be used to evaluate negating biases, not other biases.

Also, no useful to focus on a specific bias in the context of risk of bias domains

@@

## Conclusion

Triangulation is a promising developing field, somewhat hamstrung by the limited understanding of the impact of biases at the meta-epidemiological level.

\newpage

## References

### 2021-10-26 08-Discussion.Rmd
Updates

## Summary of findings (by chapter)

### Systematic review
#### Principal findings
#### Comparison with existing literature
#### Strenghts and limitations
#### Implications of this research

### CPRD
#### Principal findings
#### Comparison with existing literature
#### Strenghts and limitations
#### Implications of this research

### Individual participant data meta-analysis
#### Principal findings
#### Comparison with existing literature
#### Strenghts and limitations
#### Implications of this research

### Triangulation
#### Principal findings
#### Comparison with existing literature
#### Strenghts and limitations
#### Implications of this research

@@

Involving and engaging the public and patients has been a central theme to this thesis.

Public engagement activities included

@@

Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least one vascular dementia GWAS exists - find it and cite it here. -->

>>>>

## Lay summary

This chapter

## Chapter overview

<!-- In this final chapter I will: -->
<!--  Summarise the main findings from each chapter in relation to my two thesis hypotheses. -->
<!-- Chapter 6: Discussion -->
<!-- 162 -->
<!--  Discuss the similarities and differences between my findings and the published literature. -->
<!--  Critically evaluate the novel contributions and implications of my research. -->
<!--  Describe the limitations of my studies and consider what I would do differently given what I have learnt. -->
<!--  Recommend avenues for future research. -->

## Summary of principal findings

@@

<!-- TODO May need to tone this down a little bit -->

Involving and engaging the public and patients has been a central theme to this thesis. 
Public engagement activities included

@@

Normalisation of inclusion of preprints in systematic reviews. Wider assessment of the evidence base that exists solely as preprinted literature ()

Secondly, large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of. While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.

 <!-- TODO See notes from Pat/Emma on this -->

As a field, and as noted in Chapter \@ref(sys-rev-heading-results), the evidence synthesis theory and methods have not been sufficient developed for Mendelian randomisation studies. Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g. genetic instrumental variable analysis.)

Finally, substantial future work should be directed towards the conduct of meta-epidemiologocial studies to assess the impact of different bias in non-pbservational studies. While frameworks such as the one employed in Chapter \@ref(tri-heading) exist to allow for the production of bias-adjusted and triangulated estimates.
